Delone lattice studies in \CIII, the space of three complex variables

### 2022-12-22 C3/C3.tex
trying to use github for LaTeX
git testing
reduced.bib - remove duplicate reference C3.tex change formatting of matrices per https://github.com/dspinellis/latex-advice

\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

@@

	\citeasnoun{andrews2019b} chose to represent the scalars in the space \SVI{},
	\Svec{} (defined in the order above), as a way to create a metric space
	for the measurement of the distance between lattices. They also consider the representation of this space as the
	space of three complex dimensions, \CIII{} or {$\{c_1$}, {$c_2$}, {$c_3\}$}. 	
	In \CIII{}, in terms of the Delone scalars, a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, where the real and imaginary parts
	of each are the ``opposite'' scalars according to the definition of \citeasnoun{Delaunay1932} (see \citeasnoun{andrews2019a}).
	As a memonic device, note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).

@@

	Next we define the operators in \CIII{} that will be used in the matrix descriptions of 
	the transformations at the boundaries of the fundamental unit.\\

	\begin{table}	
		\begin{tabular}{|l|l|l|l|}
			\hline
			Operator&Usage&Result&Name \\ \hline
			$\Minus{}_r $&  $\Minus{}_r(c_j)$ & $(-x_j, -x_j+y_j)$ & Minus real \\ \hline
			$\Minus{}_i $ & $\Minus{}_i(c_j)$ & $(x_j-y_j,-y_j) $ & Minus imag\\ \hline
			$\textfrak{P}_r$ & $ \textfrak{P}_r(c_j)$ & $(x_j, x_j)$ & Plus real\\ \hline
			$\textfrak{P}_i$ &  $\textfrak{P}_i(c_j)$  & $(y_j, y_j)$ & Plus imag\\ \hline
			$\Re$ &  $\Re(c_j)$ & $x_j$ & Real \\ \hline
			$\Im$  &$ \Im(c_j)$ & $y_j$ & Imaginary \\ \hline

		\end{tabular}

@@

$\begin{bmatrix}
\textrm{i}\Re{} & \Plus{}_i & \Re{} \\
0 & \Minus{}_i & 0 \\
\textrm{i}\Im{} & \Plus{}_i & \Im{}
\end{bmatrix}$
%
$\begin{bmatrix}
\textrm{i}\Im{} & \Plus{}_i &  \Im{} \\
0 & \Minus{}_i & 0 \\
\textrm{i}\Re{} & \Plus{}_ri& \Re{} \\
\end{bmatrix}$ 
%
$\begin{bmatrix}
\Re{} &\Plus{}_i &   \textrm{i}\Re{} \\
0 & \Minus{}_i &  0 \\
\Im{} &\Plus{}_i & \textrm{i}\Im{}
\end{bmatrix}	$ 
%
$\begin{bmatrix}
\Im{} & \Plus{}_i & \textrm{i}\Im{} \\
0 &\Minus{}_i &  0 \\
\Re{} & \Plus{}_i &  \textrm{i}\Re{} \\
\end{bmatrix}$ \\

@@

\textrm{i}\Re{} & \Re{} & \Plus{}_r \\
\textrm{i}\Im{} & \Im{}& \Plus{}_r  \\
0 & 0& \Minus{}_r  \\
\end{bmatrix}$
%
$\begin{bmatrix}
\textrm{i}\Im{} &  \Im{} & \Plus{}_r \\
\textrm{i}\Re{} & \Re{} & \Plus{}_r \\
0 & 0 & \Minus{}_r \\
\end{bmatrix}$ 
%
$\begin{bmatrix}
\Re{} &   \textrm{i}\Re{} &\Plus{}_r \\
\Im{} & \textrm{i}\Im{}&\Plus{}_r \\
0  &  0 & \Minus{}_r \\
\end{bmatrix}	$ 
%
$\begin{bmatrix}
\Im{} & \textrm{i}\Im{} & \Plus{}_r \\
\Re{} &  \textrm{i}\Re{} & \Plus{}_r \\
0 &  0 &\Minus{}_r \\
\end{bmatrix}$ \\

@@

\textrm{i}\Re{} & \Re{} & \Plus{}_i \\
\textrm{i}\Im{} & \Im{}& \Plus{}_i \\
0 & 0 & \Minus{}_i 
\end{bmatrix}$
%
$\begin{bmatrix}
\textrm{i}\Im{} &  \Im{} & \Plus{}_i \\
\textrm{i}\Re{} & \Re{} & \Plus{}_i \\
0 & 0 & \Minus{}_i \\
\end{bmatrix}$ 
%
$\begin{bmatrix}
\Re{} &   \textrm{i}\Re{}  &\Plus{}_i \\
\Im{} & \textrm{i}\Im{} &\Plus{}_i \\
0 &  0 & \Minus{}_i \\
\end{bmatrix}	$ 
%
$\begin{bmatrix}
\Im{} & \textrm{i}\Im{} & \Plus{}_i \\
\Re{} &  \textrm{i}\Re{} & \Plus{}_i \\
0 &  0 &\Minus{}_i 
\end{bmatrix}$ \\

@@

\citeasnoun{Delaunay1932} does not consider the boundary transformations 
in detail. However, he uses them to define the process of Selling reduction. 
For example in \SVI{}, he lists the following as one of the possible results 
for a transformation on \si{}.
\SvecA{}
The third matrix above (the third boundary transform for $s_1$) implements this operation and interchanges the
real part of \ciii{} and the imaginary part of \cii{}.
~\\
	$\begin{bmatrix}
\Minus{}_r & 0 & 0 \\
\Plus{}_r &  \Re{} & \textrm{i}\Re{} \\
\Plus{}_r & \Im{} &\textrm{i}\Im{}
\end{bmatrix}	$
\\

>>>>

\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
%\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

%xxxxxx just for testing github % 2

@@

	\citeasnoun{andrews2019b} chose to 
	represent the scalars in the space \SVI{},
	\Svec{} (defined in the order above), 
	as a way to create a metric space
	for the measurement of the distance between lattices. T
	hey also consider the representation of this space as the
	space of three complex dimensions, \CIII{} or 
	{$\{c_1$}, {$c_2$}, {$c_3\}$}.

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of \citeasnoun{Delaunay1932} (see \citeasnoun{andrews2019a}).
	As a memonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).

@@

	Next we define the operators in \CIII{} t
	hat will be used in the matrix descriptions of 
	the transformations at the boundaries of the fundamental unit.\\

\begin{table}	
	\begin{tabular}{|l|l|l|l|}
\toprule
	Operator
						&Usage	
													&Result	
																			&Name\\
\midrule
	$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
	$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
	$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
	$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
	$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
	$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\
\bottomrule
	\end{tabular}

@@

$\begin{bmatrix}
	\textrm{i}\Re{}	& \Plus{}_i		& \Re{} \\
	0				& \Minus{}_i	& 0 \\
	\textrm{i}\Im{}	& \Plus{}_i		& \Im{}
\end{bmatrix}$
%
$\begin{bmatrix}
	\textrm{i}\Im{}	& \Plus{}_i		&  \Im{} \\
	0				& \Minus{}_i	& 0 \\
	\textrm{i}\Re{}	& \Plus{}_ri	& \Re{} \\
\end{bmatrix}$ 
%
$\begin{bmatrix}
	\Re{}	&\Plus{}_i		&   \textrm{i}\Re{} \\
	0		& \Minus{}_i	&  0 \\
	\Im{}	&\Plus{}_i		& \textrm{i}\Im{}
\end{bmatrix}	$ 
%
$\begin{bmatrix}
	\Im{}	& \Plus{}_i	& \textrm{i}\Im{} \\
	0		&\Minus{}_i	&  0 \\
	\Re{}	& \Plus{}_i	&  \textrm{i}\Re{} \\
\end{bmatrix}$ \\

@@

	\textrm{i}\Re{}	& \Re{}	& \Plus{}_r \\
	\textrm{i}\Im{}	& \Im{}	& \Plus{}_r  \\
	0				& 0		& \Minus{}_r  \\
\end{bmatrix}$
%
$\begin{bmatrix}
	\textrm{i}\Im{}	&  \Im{}	& \Plus{}_r \\
	\textrm{i}\Re{}	& \Re{}		& \Plus{}_r \\
	0				& 0			& \Minus{}_r \\
\end{bmatrix}$ 
%
$\begin{bmatrix}
	\Re{}	&   \textrm{i}\Re{}	&\Plus{}_r \\
	\Im{}	& \textrm{i}\Im{}	&\Plus{}_r \\
	0 		&  0				& \Minus{}_r \\
\end{bmatrix}	$ 
%
$\begin{bmatrix}
	\Im{}	& \textrm{i}\Im{}	& \Plus{}_r \\
	\Re{}	&  \textrm{i}\Re{}	& \Plus{}_r \\
	0		&  0				&\Minus{}_r \\
\end{bmatrix}$ \\

@@

	\textrm{i}\Re{}	& \Re{}	& \Plus{}_i \\
	\textrm{i}\Im{}	& \Im{}	& \Plus{}_i \\
	0				& 0		& \Minus{}_i 
\end{bmatrix}$
%
$\begin{bmatrix}
	\textrm{i}\Im{}	&  \Im{}	& \Plus{}_i \\
	\textrm{i}\Re{}	& \Re{}		& \Plus{}_i \\
	0				& 0			& \Minus{}_i \\
\end{bmatrix}$ 
%
$\begin{bmatrix}
	\Re{}	&   \textrm{i}\Re{} &\Plus{}_i \\
	\Im{}	& \textrm{i}\Im{}	&\Plus{}_i \\
	0		&  0				& \Minus{}_i \\
\end{bmatrix}	$ 
%
$\begin{bmatrix}
	\Im{}	& \textrm{i}\Im{}	& \Plus{}_i \\
	\Re{}	&  \textrm{i}\Re{}	& \Plus{}_i \\
	0		&  0				&\Minus{}_i 
\end{bmatrix}$ \\

@@

\citeasnoun{Delaunay1932} does not consider the boundary transformations 
in detail. However, he uses them to define the process of Selling reduction. 
For example in \SVI{}, he lists the following as one of the possible results 
for a transformation on \si{}.
\SvecA{}
The third matrix above (the third boundary transform for $s_1$) implements this operation and interchanges the
real part of \ciii{} and the imaginary part of \cii{}.

\begin{center}
		$\begin{bmatrix}
\Minus{}_r	& 0			& 0 \\
\Plus{}_r	&  \Re{}	& \textrm{i}\Re{} \\
\Plus{}_r	& \Im{}		&\textrm{i}\Im{}
\end{bmatrix}	$
\end{center}
